Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-03 testbed.tex
testbed

% MAC and Hostname file
\Suppressnumber\begin{lstlisting}[]
<@\textcolor{gray}{\$\{ROOTDIR\}/home/pi/.rasp\_config/nodes.csv}@>
<@\textcolor{gray}{
---------------------------------------------------------------}
\Reactivatenumber @>
# Ethernet MAC    Hostname
b8:27:eb:5b:da:20 rasp_00
b8:27:eb:7b:c3:91 rasp_01
b8:27:eb:54:9c:64 rasp_02
b8:27:eb:95:bd:11 rasp_03
\end{lstlisting}
\FloatBarrier

% Set hostname
\Suppressnumber\begin{lstlisting}[]
<@\textcolor{gray}{\$\{ROOTDIR\}/home/pi/.rasp\_config/set\_hostname}@>
<@\textcolor{gray}{
---------------------------------------------------------------}
\Reactivatenumber @>
#!/usr/bin/env bash
mac=$(cat /sys/class/net/eth0/address)
hostname=$(grep $mac nodes.csv | cut -f2 -d' ')

@@

Call set\_hostname script at startup. We insert a line of code to call script in rc.local just after the initial comments (i.e. lines starting with \#).
\begin{lstlisting}[]
# line_number=$(egrep -n -m1 "(^[^#])|(^$)" ${ROOTDIR}/etc/rc.local | cut -d: -f1)
# sed -i "${line_number}c bash /home/pi/.rasp_config/set_hostname" ${ROOTDIR}/etc/rc.local
\end{lstlisting}
\FloatBarrier
%$ line="bash /home/pi/.rasp_config/set_hostname"
%# awk -v text="$line" '!/^#/ && !p {print text; p=1} 1' ${ROOTDIR}/etc/rc.local > <@ \Suppressnumber @>
%    ${ROOTDIR}/etc/rc.local <@ \Reactivatenumber @>

@@

% CHROOT to OS image
\begin{lstlisting}[]
# cd $ROOTDIR
# cp /etc/resolv.conf etc/resolv.conf
# cp /usr/bin/qemu-arm-static usr/bin
# mount -t proc proc proc/
# mount --rbind /sys sys/
# mount --rbind /dev dev/
# mount --rbind /run run/
# chroot ${ROOTDIR} /usr/bin/qemu-arm-static /bin/bash

ALTERNATIVE:
# proot -q qemu-arm-static -S ${ROOTDIR}
\end{lstlisting}
\FloatBarrier

@@

@@

% Setup initramfs
\begin{lstlisting}[]
# echo "overlay" > /etc/initramfs-tools/modules
# cp ${OVERLAYROOTDIR}/hooks-overlay /etc/initramfs-tools/hooks/
# cp ${OVERLAYROOTDIR}/init-bottom-overlay /etc/initramfs-tools/scripts/init-bottom/
\end{lstlisting}
\FloatBarrier

% Create an initramfs
\begin{lstlisting}[]
# mkinitramfs -o /boot/init.gz
\end{lstlisting}
\FloatBarrier

>>>>

% MAC and Hostname file
\Suppressnumber\begin{lstlisting}[]
<@\textcolor{gray}{\$\{ROOTDIR\}/home/pi/rasp\_config/nodes.csv}@>
<@\textcolor{gray}{
---------------------------------------------------------------}
\Reactivatenumber @>
# Ethernet MAC    Hostname
b8:27:eb:5b:da:20 rasp_00
b8:27:eb:7b:c3:91 rasp_01
b8:27:eb:54:9c:64 rasp_02
b8:27:eb:95:bd:11 rasp_03
\end{lstlisting}
\FloatBarrier

% Set hostname
\Suppressnumber\begin{lstlisting}[]
<@\textcolor{gray}{\$\{ROOTDIR\}/home/pi/rasp\_config/set\_hostname}@>
<@\textcolor{gray}{
---------------------------------------------------------------}
\Reactivatenumber @>
#!/usr/bin/env bash
mac=$(cat /sys/class/net/eth0/address)
hostname=$(grep $mac nodes.csv | cut -f2 -d' ')

@@

Call set\_hostname script at startup. We insert a line of code to call script in rc.local just after the initial comments (i.e. lines starting with \#).
\begin{lstlisting}[]
# line_number=$(egrep -n -m1 "(^[^#])|(^$)" ${ROOTDIR}/etc/rc.local | cut -d: -f1)
# sed -i "${line_number}c bash /home/pi/rasp_config/set_hostname" ${ROOTDIR}/etc/rc.local
\end{lstlisting}
\FloatBarrier
%$ line="bash /home/pi/.rasp_config/set_hostname"
%# awk -v text="$line" '!/^#/ && !p {print text; p=1} 1' ${ROOTDIR}/etc/rc.local > <@ \Suppressnumber @>
%    ${ROOTDIR}/etc/rc.local <@ \Reactivatenumber @>

@@

% CHROOT to OS image
\begin{lstlisting}[]
# cd $ROOTDIR
# cp /etc/resolv.conf etc/resolv.conf
# cp /usr/bin/qemu-arm-static usr/bin
# mount -t proc proc proc/
# mount --rbind /sys sys/
# mount --rbind /dev dev/
# proot -q qemu-arm-static -S ${ROOTDIR}

ALTERNATIVE:
# chroot ${ROOTDIR} /usr/bin/qemu-arm-static /bin/bash
\end{lstlisting}
\FloatBarrier

% Optionally, we may create a unique prompt to indicate we have changed root
\begin{lstlisting}[]
# export PS1="(chroot) $PS1"
\end{lstlisting}
\FloatBarrier

@@

% Setup initramfs
\begin{lstlisting}[]
# cp ${OVERLAYROOTDIR}/hooks-overlay /etc/initramfs-tools/hooks/
# cp ${OVERLAYROOTDIR}/init-bottom-overlay /etc/initramfs-tools/scripts/init-bottom/
# echo "overlay" > /etc/initramfs-tools/modules
\end{lstlisting}
\FloatBarrier

@@

% Create an initramfs
\begin{lstlisting}[]
# mkinitramfs -o /boot/init.gz
# mkinitramfs -o /boot/init.gz -k 4.4.11+
\end{lstlisting}
\FloatBarrier

\subsection{Write image}

% Exit chroot, umount, and write to memory card
\begin{lstlisting}[]
# exit
# cd ..
# umount --recursive ${ROOTDIR}
# losetup -d WHICH_NUMBE.img of=/dev/mmcblk0 bs=4MR
# dd if=${IMAGE}.img of=/dev/mmcblk0 bs=4M
\end{lstlisting}
\FloatBarrier
